First steps towards a formalization of Forcing

### 2018-08-18 LSFA/related.tex
final sin revisar, falta Jaber

Finally, there are some forcing-related formalizations in the theory
of types. Most relevant is the work by K.~Quirin \cite{Quirin}, where
a sheaf-theoretic initial approach to forcing is implemented in
Coq. This language is extremely different to the standard approach of
constructing models of $\ZFC$, and it might be difficult (once the
forcing machinery is set) to translate results in the literature using
ctms to this one. In any case, the translation to set theory of what
Quirin accomplishes is to define a generic extension (where $\CH$
should fail) and to construct a set $K$ (a candidate counterexample)
and injections $\N\to K$ and $K\to\R$. But the most important part,
that is, that there are no surjections

\begin{enumerate}
\item Jaber et al.\ \cite{jaber:hal-01319066}.
\end{enumerate}
%We continue with a brief description of the Isabelle framework.

>>>>

There are some forcing-related formalizations in the theory
of types. Most relevant is the work by K.~Quirin \cite{Quirin}, where
a sheaf-theoretic initial approach to forcing is implemented in
Coq. This language is extremely different to the standard approach of
constructing models of $\ZFC$, and it might be difficult (once the
forcing machinery is set) to translate results in the literature using
ctms to this one. In any case, the translation to set theory of what
Quirin accomplishes is to define a generic extension (where $\CH$
should fail) and to construct a set $K$ (a candidate counterexample)
and injections $\N\hookrightarrow K$ and $K\hookrightarrow\R$. But the
most important part, that is, that there are no surjections 
$\N\twoheadrightarrow K$ and $K\twoheadrightarrow\R$, is left for a future
work. % Finally,  Jaber et al.\ \cite{jaber:hal-01319066}
